noam_data_exploration_v1

### 2024-08-16 noam_data_exploration_v3.Rmd

# playing around with stuff here - ignore for now
x <- subset(data_subset, location == "lter_1_backreef_algae_transect_1_quad_1")
year_combinations <- expand.grid(Year1 = x$year, Year2 = x$year)
year_combinations <- year_combinations[year_combinations$Year1 != year_combinations$Year2, ] # filter out year 1 == year 2
year_combinations$Year_Difference <- abs(year_combinations$Year1 - year_combinations$Year2) # find difference in years
year_combinations$location <- rep("lter_1_backreef_algae_transect_1_quad_1", nrow(year_combinations))
year_combinations$bray <- NA
for(i in 1:nrow(year_combinations)){
  subset(x)
}

>>>>

# playing around with stuff here - ignore for now
x <- subset(data_subset, location == "lter_1_backreef_algae_transect_1_quad_1")
year_combinations <- expand.grid(Year1 = x$year, Year2 = x$year)
year_combinations <- year_combinations[year_combinations$Year1 != year_combinations$Year2, ] # filter out year 1 == year 2
year_combinations$Year_Difference <- abs(year_combinations$Year1 - year_combinations$Year2) # find difference in years
year_combinations$location <- rep("lter_1_backreef_algae_transect_1_quad_1", nrow(year_combinations))
year_combinations$bray <- NA
for(i in 1:nrow(year_combinations)){
  subset(x, year == year_combinations[i,1] | year_combinations[i,2])
}
